Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-06 paper.qmd
Updated spacing
Try to reduce the number of pages

\spacingset{1.0} <!--% command in JASA style, comment to go back to double spacing-->

@@

```{r}
#| label: fig-NLDR-variety
#| echo: false
#| fig-cap: "Eight different NLDR representations of the same data. Different techniques and different parameter choices are used. Researchers may have seen any of these in their analysis of this data, depending on their choice of method, or typical parameter choice. Would they make different decisions downstream in the analysis depending on which version seen? Which is the most accurate representation of the structure in high dimensions?"
#| fig-width: 8
#| fig-height: 4
#| out-width: 100%
# (a) UMAP (n_neighbors = 30, min_dist = 0.3), (b) UMAP (n_neighbors = 5, min_dist = 0.01), (c) UMAP (n_neighbors = 15, min_dist = 0.99), (f) tSNE (perplexity = 5), (g) tSNE (perplexity = 30), (l) TriMAP (n_inliers = 12, n_outliers = 4, n_random = 3), (q) PaCMAP (n_neighbors = 30, init = random, MN_ratio = 0.9, FP_ratio = 5)
nldr1 + nldr2 + nldr3 + nldr4 +
  nldr5 + nldr6 + nldr7 + nldr8 +
  plot_layout(ncol = 4)
```

>>>>

\spacingset{2.0} <!--% command in JASA style, comment to go back to double spacing-->

@@

```{r}
#| label: fig-NLDR-variety
#| echo: false
#| fig-cap: "Eight different NLDR representations of the same data. Different techniques and different parameter choices are used. Researchers may have seen any of these in their analysis of this data, depending on their choice of method, or typical parameter choice. Would they make different decisions downstream in the analysis depending on which version seen? Which is the most accurate representation of the structure in high dimensions?"
#| fig-width: 8
#| fig-height: 4
#| out-width: 100%
#| fig-pos: H
# (a) UMAP (n_neighbors = 30, min_dist = 0.3), (b) UMAP (n_neighbors = 5, min_dist = 0.01), (c) UMAP (n_neighbors = 15, min_dist = 0.99), (f) tSNE (perplexity = 5), (g) tSNE (perplexity = 30), (l) TriMAP (n_inliers = 12, n_outliers = 4, n_random = 3), (q) PaCMAP (n_neighbors = 30, init = random, MN_ratio = 0.9, FP_ratio = 5)
nldr1 + nldr2 + nldr3 + nldr4 +
  nldr5 + nldr6 + nldr7 + nldr8 +
  plot_layout(ncol = 4)
```
